Grove: A Convergent Collaborative Structure-Editor Calculus

### 2021-01-21 grove-paper.tex

@@

https://crdt.tech/papers.html
[35]
    Mahsa Najafzadeh, Marc Shapiro, and Patrick Eugster. Co-design and verification of an available file system. In 19th International Conference on Verification, Model Checking, and Abstract Interpretation, VMCAI 2018, pages 358--381. Springer LNCS volume 10747, January 2018. [ bib | DOI | .pdf ]

        Keywords: trees

[41]
    Martin Kleppmann and Alastair R Beresford. A conflict-free replicated JSON datatype. IEEE Transactions on Parallel and Distributed Systems, 28(10):2733--2746, April 2017. [ bib | DOI | arXiv ]

        Keywords: trees

[67]
    Vinh Tao, Marc Shapiro, and Vianney Rancurel. Merging semantics for conflict updates in geo-distributed file systems. In 8th ACM International Systems and Storage Conference, SYSTOR 2015. ACM, May 2015. [ bib | DOI | .pdf ]

        Keywords: trees

[95]
    Mehdi Ahmed-Nacer, Stéphane Martin, and Pascal Urso. File system on CRDT. Research Report RR-8027, INRIA, July 2012. [ bib | arXiv | http ]

        Keywords: trees

[103]
    Stéphane Martin, Pascal Urso, and Stéphane Weiss. Scalable XML collaborative editing with undo. In On the Move to Meaningful Internet Systems (OTM), pages 507--514. Springer LNCS volume 6426, October 2010. [ bib | DOI | arXiv ]

        Keywords: trees, undo

>>>>

A commutative replicated data type for cooperative editing
  \url{https://hal.inria.fr/inria-00445975/document}
  Describes TreeDoc but this uses a document model that is a list (tree is just how it is implemented)

Logoot : a Scalable Optimistic Replication Algorithm for Collaborative Editing on P2P Networks
  \url{http://pagesperso.lina.univ-nantes.fr/~molli-p/pmwiki/uploads/Main/weiss09.pdf}

Specification and Complexity of Collaborative Text Editing
  \url{https://www.microsoft.com/en-us/research/wp-content/uploads/2016/07/podc16-complete.pdf}

LSEQ: an Adaptive Structure for Sequences in Distributed Collaborative Editing,
  \url{https://hal.archives-ouvertes.fr/file/index/docid/921633/filename/fp025-nedelec.pdf}

Data consistency for P2P collaborative editing
  \url{https://hal.archives-ouvertes.fr/file/index/docid/108523/filename/OsterCSCW06.pdf}

Interleaving anomalies in collaborative text editors
  \url{https://martin.kleppmann.com/papers/interleaving-papoc19.pdf}

Moving Elements in List CRDTs
  \url{https://martin.kleppmann.com/papers/list-move-papoc20.pdf}

A highly-available move operation for replicated trees and distributed filesystems
  \url{https://martin.kleppmann.com/papers/move-op.pdf}

@@

https://crdt.tech/papers.html

Mahsa Najafzadeh, Marc Shapiro, and Patrick Eugster. Co-design and verification of an available file system. In 19th International Conference on Verification, Model Checking, and Abstract Interpretation, VMCAI 2018, pages 358--381. Springer LNCS volume 10747, January 2018. [ bib | DOI | .pdf ]
  \url{http://dx.doi.org/10.1007/978-3-319-73721-8_17}
  https://pages.lip6.fr/Marc.Shapiro/papers/VMCAI-2018-filesys.pdf

Martin Kleppmann and Alastair R Beresford. A conflict-free replicated JSON datatype. IEEE Transactions on Parallel and Distributed Systems, 28(10):2733--2746, April 2017. [ bib | DOI | arXiv ]
  http://dx.doi.org/10.1109/TPDS.2017.2697382
  http://arxiv.org/abs/1608.03960

Vinh Tao, Marc Shapiro, and Vianney Rancurel. Merging semantics for conflict updates in geo-distributed file systems. In 8th ACM International Systems and Storage Conference, SYSTOR 2015. ACM, May 2015. [ bib | DOI | .pdf ]
  http://dx.doi.org/10.1145/2757667.2757683
  https://pages.lip6.fr/Marc.Shapiro/papers/geodistr-FS-Systor-2015.pdf

Mehdi Ahmed-Nacer, Stéphane Martin, and Pascal Urso. File system on CRDT. Research Report RR-8027, INRIA, July 2012. [ bib | arXiv | http ]
  http://arxiv.org/abs/1207.5990
  https://hal.inria.fr/hal-00720681/

Stéphane Martin, Pascal Urso, and Stéphane Weiss. Scalable XML collaborative editing with undo. In On the Move to Meaningful Internet Systems (OTM), pages 507--514. Springer LNCS volume 6426, October 2010. [ bib | DOI | arXiv ]
  \url{http://dx.doi.org/10.1007/978-3-642-16934-2_37}
  http://arxiv.org/abs/1010.3615
